Scan-Centric, Frequency-Based Method for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2022-03-18 doc/peakcharacterization_manuscript.Rmd
putting all of the chi-square test results together and then within the manuscript

figure_count = dn_counter$new("Figure ")
```

@@

@@

## Methods

@@

@@

Figure X compares the HPD regions detected using the method from Mitchell et al., and their correspondence with high FSD peaks for one sample (the other comparisons are in Supplemental materials).
Based on this comparison, the high FSD peaks are indeed HPD sites and should be removed before assignment.
However, the FSD does not depend on calculating a sliding window based density, but is merely a product of those peaks across multiple scans that span a wider range frequency range than expected based on the peaks in the data. We also note that we do expect higher m/z standard deviations at higher m/z, but the frequency based method does not suffer the same effect, due to the offsets of frequency points being constant.

@@

>>>>

figure_count = dn_counter$new("Figure ")
table_count = dn_counter$new("Table ")
```

@@

## Keywords

@@

@@

```{r increment_hpd}
figure_count$increment("hpd_fsd")
```

@@

`r figure_count$label_text("hpd_fsd")` compares the HPD regions detected using the method from Mitchell et al., and their correspondence with high FSD peaks for one sample (the other comparisons are in Supplemental materials).
`r table_count$label_text("hpd_fsd")` summarizes the results of Chi-square tests using contingency tables of HPD and high FSD peaks.
Based on this comparison, the high FSD peaks are indeed HPD sites and should be removed before assignment.
However, the FSD does not depend on calculating a sliding window based density, but is merely a product of those peaks across multiple scans that span a wider range frequency range than expected based on the peaks in the data. We also note that we do expect higher m/z standard deviations at higher m/z, but the frequency based method does not suffer the same effect, due to the offsets of frequency points being constant.

```{r hpd_fsd, dn_id = figure_count}
tar_load(hpd_plots_49lipid)
hpd_plots_49lipid
```

`r figure_count$label_text("hpd_fsn")`.
Comparison of HPD and high FSD sites in the lipid 49 sample.
Black are the original fully characterized peaks.
Red indicates peaks within HPD sites detected using the XCalibur peak sets.
Blue indicates peaks that had abnormally high FSD values.

`r table_count$label_text("hpd_fsn")`.
Chi-square statistics from contingency tables of shared presence and absence of peaks in HPD sites and labeled as high FSD.

```{r hpd_fsd_table}
tar_load(hpd_chisq_all)
sci_formatter = 
hpd_chisq_table = hpd_chisq_all %>%
  dplyr::select(sample, p.value, statistic) %>%
  flextable() %>%
  set_formatter(p.value = function(x){
    formatC(x, format = "e", digits = 2)
  }) %>%
  colformat_double(digits = 1, j = 3) %>%
  autofit()
```

@@

## Discussion

## Materials and Methods

## Conclusions
